DATA 621 - Business Analytics and Data Mining

### 2020-12-02 Final_project/Final Project Paper - Group 2.Rmd
Clean up Linear 1 start linear 2

# Convert trending_date to a date
full_set[, trending_date := as.IDate(trending_date, format = "%y.%d.%m")]

@@

### Model 1: Linear Regression
Keeping country as a predictor is of less interest. It will most likely track
some measure of population. It is of more interest to see if there are
differences in the factors between countries. To capture this by interactions
would be combinatorially unfeasible. Instead, five models will be run, each on
a country specific subset. This is akin to a manual implementation of a rules
based regression model

```{r modelLinear1, cache = 2L}
# Using stepAIC means no cross-validation. Train on entire dataset.
trC <- trainControl(method = 'none', allowParallel = TRUE)
cl <- makePSOCKcluster(5)
registerDoParallel(cl)
set.seed(181)
for (ct in unique(fullExtract$country)) {
  linMod <- train(views ~ likes + dislikes + comments + tags + category_id +
                    comments_disabled + ratings_disabled +
                    video_error_or_removed + perfect + lkratio,
                  data = fullExtract[country == ct],
                  family = gaussian(link = 'identity'), direction = 'both',
                  method = 'glmStepAIC', trace = 0, trControl = trC)
  assign(paste0('linMod', ct), linMod)
}
stopCluster(cl)
lM1US <- linModUS$finalModel
lM1CA <- linModCA$finalModel
lM1GB <- linModGB$finalModel
lM1FR <- linModFR$finalModel
lM1DE <- linModDE$finalModel
clM1US <- linModUS$finalModel$coefficients
clM1CA <- linModCA$finalModel$coefficients
clM1GB <- linModGB$finalModel$coefficients
clM1FR <- linModFR$finalModel$coefficients
clM1DE <- linModDE$finalModel$coefficients
nclM1US <- names(clM1US)
nclM1CA <- names(clM1CA)
nclM1GB <- names(clM1GB)
nclM1FR <- names(clM1FR)
nclM1DE <- names(clM1DE)
nnclM1US <- length(nclM1US)
nnclM1CA <- length(nclM1CA)
nnclM1GB <- length(nclM1GB)
nnclM1FR <- length(nclM1FR)
nnclM1DE <- length(nclM1DE)
length(nclM1US) <- 22
length(nclM1GB) <- 22
length(nclM1FR) <- 22
length(nclM1DE) <- 22
```

@@

>>>>

# Convert trending_date to a date and views to double since the sum > 2^31
full_set[, `:=`(trending_date = as.IDate(trending_date, format = "%y.%d.%m"),
                views = as.double(views))]

@@

### Multiple Linear Regression
Linear regression may be the best known algorithm used when analyzing a
continuous numeric outcome. It searches for a linear relationship of the
predictors that minimizes the squared error between the "predictor" function and
the observations [@Sheather2009AMA].

#### Model 1: Model by Country
The first linear regression model will actually be a rule-based set of models.
The hypothesis is that using country as a factor will most likely simply track
some measure of population. It is of more interest to see if there are
differences in the factors between countries. To capture this by interactions
would be combinatorially unfeasible. Instead, five models will be run, each on
a country specific subset. This is akin to a manual implementation of a rules
based regression model

```{r modelLinear1, cache = 2L}
# Using stepAIC means no cross-validation. Train on entire dataset.
trC <- trainControl(method = 'none', allowParallel = TRUE)

# Capture the unique country codes
ctCodes <- unique(fullExtract$country)
cl <- makePSOCKcluster(5)
registerDoParallel(cl)
set.seed(181)
maxPars <- 0
for (ct in ctCodes) {
  # Run the StepAIC algorithm inside the loop
  linMod <- train(views ~ likes + dislikes + comments + tags + category_id +
                    comments_disabled + ratings_disabled +
                    video_error_or_removed + perfect + lkratio,
                  data = fullExtract[country == ct],
                  family = gaussian(link = 'identity'), direction = 'both',
                  method = 'glmStepAIC', trace = 0, trControl = trC)

  # Assign the outcomes to dynamically "named" variables inside the loop
  assign(paste0('linMod', ct), linMod)
  assign(paste0('lM1', ct), linMod$finalModel)
  assign(paste0('clM1', ct), linMod$finalModel$coefficients)
  assign(paste0('nclM1', ct), names(linMod$finalModel$coefficients))
  assign(paste0('nnclM1', ct), length(names(linMod$finalModel$coefficients)))
  if ((length(names(linMod$finalModel$coefficients))) > maxPars) {
    maxPars <- length(names(linMod$finalModel$coefficients))
  }
}
stopCluster(cl)

# R has difficulty with ragged arrays, so override the lengths to pad with NAs
# Splitting for 80 char convenience
length(nclM1US) <- length(nclM1GB) <- length(nclM1FR) <- maxPars
length(nclM1DE) <- length(nclM1CA) <- maxPars
```

@@

### Model 2: Linear Regression Globally
While a rule-based model has the ability to fit data more closely based on those
rules, it adds a significant amount of both parameter and model error
[@Adler2015EtP; Adler2014For]. To test this hypothesis, we will run the same
linear regression, but on the global results: the sum of all the numeric values
by country except tags count. The other factors beside country deal with the
video itself, like tag count, therefore they are identical across the countries.

```{r m2Prep}
globalExtract <- unique(fullExtract[,
                                    .(views = sum(views),
                                      likes = sum(likes),
                                      dislikes = sum(dislikes),
                                      comments = sum(comments),
                                      tags = tags,
                                      category_id,
                                      comments_disabled,
                                      ratings_disabled,
                                      video_error_or_removed),
                                    keyby = title])

```
